---
title: "Fml Assignment-1"
author: "Samiha"
date: "2024-01-29"
output:
  pdf_document: default
  html_document: default
---

### 1.Summary: This is an analysis on the in built Iris dataset. I have shown the descriptive statistics of the variables, transformation of a quantitative variable and scatter plot for both quantatitive and qualitative variables.

```{r}
library(tinytex)
library(caret)
library(lattice)
library(ggplot2)
library(latex2exp)
```



2.The in built data set Iris is used here
```{r}
ds<-iris
```


3.The descriptive statistics for a selection of quantitative and categorical variables
```{r}
summary(ds)
str(ds)
dim(ds)

```


4.The transformation of the quantitative variable sepal.length variable to logical
```{r}
as.logical(ds$Sepal.Length)
```


5.The table for the following variables- petal.length and species
```{r}
Table<-table(ds$Petal.Length,ds$Species)
head(Table)
```


The scatter plot for following variables- petal.length and species
```{r}
plot(ds$Petal.Length,ds$Species)
```

The table is for the following variables- Sepal.Length and Sepal.Width
```{r}
Box<-table(ds$Sepal.Length,ds$Sepal.Width)
head(Box)
```



The scatter plot is for following variables- Sepal.Length,Sepal.Width
```{r}
plot(ds$Sepal.Length,ds$Sepal.Width)
```

